Donor Preferences in Canadian Political Financing

### 2024-12-04 paper/paper.qmd
bolded a few words

The models are specified as follows for the Ontario and Federal Models:

@@

- \(\log(\text{Total Donations}_i)\): The logarithm of total donations received by party \(i\) in a given year.\\
- \(\text{Recipient\_in\_Power}_i\): A binary variable indicating if party \(i\) was in power.\\
- \(\text{Party\_Size}_i\): A binary variable indicating if party \(i\) is a major party.\\
- \(\text{Election\_Year}_i\): A binary variable indicating if it was an election year.\\
- \(\epsilon_i\): The error term.
```
For the Conservative and Liberal parties, we included an interaction
term:

@@

Where:
- \(\text{Party}_i\): A binary variable indicating 1 for Conservative, 0 for Liberal.\\
```
Each model uses the logarithm of total donations (Log_Total_Donations)
as the dependent variable to stabilize variance and normalize the
distribution of donation amounts. Predictor variables include binary
indicators for whether the party was in power (In_Power), the size of
the party (Party_Size), and whether the donation was made during an
election year (Election_Year).

The specialized model for Conservative and Liberal parties includes an
additional binary variable (Party) and an interaction term (In_Power \*
Party) to capture the combined effect of power status and party type on
donation amounts.

@@

## Ontario Results 
In the Ontario model, Party_Size is a significant predictor of total donations, with a coefficient of 2.956 (standard error = 0.485, p < 0.001). This indicates that major parties in Ontario receive significantly higher total donations than minor parties, highlighting the influence of party prominence on fundraising success.

@@

## Federal Results
In the Federal model, Party_Size remains a significant predictor, with a coefficient of 3.450 (standard error = 0.259, p < 0.001). This reinforces the importance of party size in attracting donations at the federal level.

@@

## Conservative/Liberal Results
In the Conservative/Liberal model, In_Power has a significant positive effect, with a coefficient of 1.202 (standard error = 0.497, p = 0.01827). Additionally, the interaction term In_Power × Party is significantly negative, with a coefficient of -1.718 (standard error = 0.711, p = 0.01845). This interaction indicates that the effect of being in power on total donations varies between the Conservative and Liberal parties.

@@

```
@fig-estimates highlights the consistently strong positive effect of Party_Size on total donations in both the Ontario and Federal models, emphasizing that major parties attract significantly more donations than minor parties. It also illustrates the significant interaction effect between In_Power and Party in the Conservative/Liberal model, demonstrating the differing impact of being in power on donations for the two major parties.

>>>>

The models are specified as follows for the **Ontario and Federal
Models**:

@@

- \(\log(\text{Total Donations}_i)\): The logarithm of total donations received by party \(i\) in a given year.\\
- \(\text{Recipient\_in\_Power}_i\): A binary variable indicating if party \(i\) was in power.\\
- \(\text{Party\_Size}_i\): A binary variable indicating if party \(i\) is a major party.\\
- \(\text{Election\_Year}_i\): A binary variable indicating if it was an election year.\\
- \(\epsilon_i\): The error term.
```
For the **Conservative and Liberal parties**, we included an interaction
term:

@@

- \(\text{Party}_i\): A binary variable indicating 1 for Conservative, 0 for Liberal.\\
```
The specialized model for Conservative and Liberal parties includes an
additional binary variable (Party) and an interaction term (In_Power \*
Party) to capture the combined effect of power status and party type on
donation amounts.

@@

## Ontario Results

In the Ontario model, Party_Size is a significant predictor of total
donations, with a coefficient of 2.956 (standard error = 0.485, p \<
0.001). This indicates that major parties in Ontario receive
significantly higher total donations than minor parties, highlighting
the influence of party prominence on fundraising success.

@@

## Federal Results

In the Federal model, Party_Size remains a significant predictor, with a
coefficient of 3.450 (standard error = 0.259, p \< 0.001). This
reinforces the importance of party size in attracting donations at the
federal level.

@@

## Conservative/Liberal Results

In the Conservative/Liberal model, In_Power has a significant positive
effect, with a coefficient of 1.202 (standard error = 0.497, p =
0.01827). Additionally, the interaction term In_Power × Party is
significantly negative, with a coefficient of -1.718 (standard error =
0.711, p = 0.01845). This interaction indicates that the effect of being
in power on total donations varies between the Conservative and Liberal
parties.

@@

@fig-estimates highlights the consistently strong positive effect of
Party_Size on total donations in both the Ontario and Federal models,
emphasizing that major parties attract significantly more donations than
minor parties. It also illustrates the significant interaction effect
between In_Power and Party in the Conservative/Liberal model,
demonstrating the differing impact of being in power on donations for
the two major parties.
